%کلمات کلیدی انگلیسی
\latinkeywords{IRS, Double Reflection, Sum-Rate, Coordinate Descent, Gradient Descent}
%چکیده انگلیسی

\en-abstract{
This research explores the potential application of Intelligent Reflecting Surfaces (IRS) in the context of future communication networks, specifically focusing on 6G.
The study aims to optimize the weighted-sum-rate objective function for a realistic scenario involving two users.
In this scenario, the collaboration of two IRS units is considered, with a second-order reflection occurring between them.
One of the users experiences an obstacle, highlighting the need for improved network performance.
To enhance the communication network’s performance, a joint optimization approach is employed, optimizing both the passive beamforming coefficients of the IRS and the active beamforming coefficients of the antenna.
This optimization is carried out using a coordinate descent algorithm consisting of a gradient descent inside it, which iteratively refines the beamforming coefficients to maximize the overall system performance. 
The research also includes an evaluation of the Signal-to Interference-plus-Noise Ratio (SINR) improvement in the presence of the second-order reflection between the two IRS units.
The optimization process comprises several key steps.
Firstly, the Lagrangian dual transformation is applied to eliminate the logarithmic function, simplifying the optimization problem.
This transformation facilitates a more efficient and tractable optimization process.
Additionally, fractional programming techniques are employed to convert fractional terms into linear functions, further streamlining the optimization process.
These optimization techniques enable the exploration of optimal beamforming strategies and pave the way for enhanced performance in future wireless communication systems.
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}